---
title: 
author: ''
date: '2021-06-11'
slug: Testing
categories: []
tags: [MSRA]
bibliography: packages.bib
---

## Data visualization `r emo::ji("telescope")` 

One of our provided services entails the wrangling, analysis, and *meaningful visualization* of data. 

Below we present two demonstrative visualizations extracted from larger projects to highlight interactive visualizations (where the user is provided some level of involvement with the graphic). 

# Example #1: `r emo::ji("fuel_pump")`

This project included the creation of an interactive map to locate petrol stations that provide ethanol-free gasoline within the 5-state region surrounding a local car club. This group does social "runs" periodically throughout the summer months and did not have a map-based resource to help them locate these specialized gas stations while on their far-from-home "runs".  

```{r, echo=FALSE, warning=FALSE, include=FALSE}
library(leaflet)
oct <- read.csv("octane.csv")

# oct$octane <- as.factor(as.character(oct$octane))

pal2 <- colorNumeric(
  palette = "Spectral",
  reverse = TRUE,
  domain = oct$octane
)

## create leaflet map
octmap <- leaflet() %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  setView(-93.11389168, 45.08506268	,
          zoom = 8) %>%
  addTiles() %>%
  addCircles(data=oct, lng = ~long, lat = ~lat, popup = ~address, weight=10, color=~pal2(octane), opacity=1, radius=10) %>%
  addLegend("bottomright", data=oct, pal = pal2, values = ~octane)

widgetframe::frameWidget(octmap) ## trying for online

```


```{r echo=FALSE, warning=FALSE, include=FALSE}

oct$color[oct$octane == 91] <- "orange"
oct$color[oct$octane == 93] <- "lightred"
oct$color[oct$octane == 95] <- "darkred"

icons <- awesomeIcons(icon = "fire",
                      iconColor = "#000000",
                      markerColor = oct$color)

octmap2 <- leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>% 
  setView(-93.11389168, 45.08506268	,
          zoom = 8) %>%
  addTiles() %>%
  addAwesomeMarkers(data = oct, lng = ~long, lat = ~lat, icon = icons) 

widgetframe::frameWidget(octmap2) ## trying for online

```


```{r echo=FALSE, warning=FALSE}
knitr::write_bib(c(.packages(), "bookdown", "tidygeocoder"), "packages.bib")

minny <- read.csv("minny.csv")
iowa <- read.csv("iowa.csv")
sd <- read.csv("sd.csv")
wisc <- read.csv("wisc.csv")
nd <- read.csv("nd.csv")

miss <- read.csv("missing_geocodio.csv")  ## taken from geocodio
use <- miss[,c(1:11)]
colnames(use)[10] <- "lat"
colnames(use)[11] <- "long"

use$lat[use$lat == 0] <- NA
use$long[use$long == 0] <- NA

states <- rbind(minny, iowa, sd, wisc, nd, use)


library(stringr)
states$max <- as.numeric(str_sub(states$Octane, start= -3))

missing <- states[ which(is.na(states$lat) & is.na(states$long)), ]
missing <- missing[,2:9]

# write.csv(missing, "missing.csv")  ## for 3rd party lat and long estimates

```

<p align="center">
`r emo::ji("warning")` `r emo::ji("warning")` `r emo::ji("skull_and_crossbones")` **NEVER** use this map *while driving* `r emo::ji("face_with_symbols_on_mouth")` `r emo::ji("warning")` `r emo::ji("warning")` 
</p>

```{r map, echo=FALSE, warning=FALSE, include=FALSE}

pal <- colorNumeric(
  palette = "Spectral",
  reverse = TRUE,
  domain = states$max
)

puregas <- leaflet() %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  setView(-93.11389168, 45.08506268	,
          zoom = 6) %>%
  addTiles() %>%
  addCircles(data=states, lng = ~long, lat = ~lat, popup = ~paste(Name, "<br>",Street.Address, "<br>", City, State, "<br>", Phone, "<br>", "Max Octane:", max), color=~pal(max), opacity=.8) %>%
  addLegend("bottomright", data=states, pal = pal, values = ~max)

widgetframe::frameWidget(puregas) ## trying for online

```


```{r map2, echo=FALSE, warning=FALSE}

states$octane[states$max < 91] <- "less than 91"
states$octane[states$max == 91] <- "91"
states$octane[states$max > 91 & states$max < 100] <- "92 - 99"
states$octane[states$max > 99] <- "100 or more"

states$octane <- factor(states$octane, levels = c("less than 91", "91", "92 - 99", "100 or more"))

states$mapping <- as.numeric(as.character(str_sub(states$Octane, start= -1)))  ## for circle radius

pal2 <- colorFactor(
  palette = c("#0000FF", "#FFFF00", "#FF0000", "#FF00CC"),
  domain = states$octane
)

## create leaflet map
altmap <- leaflet() %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  setView(-93.11389168, 45.08506268	,
          zoom = 9) %>%
  addTiles() %>%
  addCircles(data=states, lng = ~long, lat = ~lat, weight = 1,
             radius = ~max*10, popup = ~paste(Name, "<br>",Street.Address, "<br>", City, State, "<br>", Phone, "<br>", "Max Octane:", max), fillColor=~pal2(octane), fillOpacity = .5 ) %>%
  addLegend("bottomright", data=states, pal = pal2, values = ~octane, opacity = 1)

widgetframe::frameWidget(altmap)

```

```{r missingstations, warning=FALSE, echo=FALSE, eval=FALSE}

## searchable table - taken off example pate 2/25/23

table <- states[ which(!is.na(states$lat) & !is.na(states$long)), ]

library(DT)
datatable(table[c(5,7,2,9,4,6)], rownames=FALSE, options = list(pageLength = 5))  

```

# Example #2: `r emo::ji("football")`

This project was a simple comparison of points scored by different skilled football positions for the purposes of scoring system alteration within a fantasy football leage. The extracted visual primarily highlights **data filtering** capability (note the "qb", "rb", "wr" key in the upper right corner).

## Top 20 point scorers by position (QB, WR, RB)

```{r, echo=FALSE, warning=FALSE, include=FALSE}

qb <- read.csv("qb.csv", header=FALSE, fileEncoding = "latin1")
wr <- read.csv("wr.csv", header=FALSE, fileEncoding = "latin1")
rb <- read.csv("rb.csv", header=FALSE, fileEncoding = "latin1")

## apply Phantazee scoring here

qb$yds[qb$V6 < 150] <- 0
qb$yds[qb$V6 >= 150 & qb$V6 < 200] <- 1
qb$yds[qb$V6 >= 200 & qb$V6 < 250] <- 2
qb$yds[qb$V6 >= 250 & qb$V6 < 300] <- 3
qb$yds[qb$V6 >= 300 & qb$V6 < 350] <- 4
qb$yds[qb$V6 >= 350 & qb$V6 < 400] <- 5
qb$yds[qb$V6 >= 400 & qb$V6 < 450] <- 6
qb$yds[qb$V6 >= 450 & qb$V6 < 500] <- 7
qb$yds[qb$V6 >= 500 & qb$V6 < 550] <- 8
qb$yds[qb$V6 >= 550 & qb$V6 < 600] <- 9
qb$yds[qb$V6 >= 600 & qb$V6 < 650] <- 10
qb$yds[qb$V6 >= 650 & qb$V6 < 700] <- 11

qb$tds1 <- qb$V7*3

qb$ydsr[qb$V10 < 20] <- 0
qb$ydsr[qb$V10 >= 20 & qb$V10 < 40] <- 1
qb$ydsr[qb$V10 >= 40 & qb$V10 < 60] <- 2
qb$ydsr[qb$V10 >= 60 & qb$V10 < 80] <- 3
qb$ydsr[qb$V10 >= 80 & qb$V10 < 100] <- 4
qb$ydsr[qb$V10 >= 100 & qb$V10 < 120] <- 5
qb$ydsr[qb$V10 >= 120 & qb$V10 < 140] <- 6
qb$ydsr[qb$V10 >= 140 & qb$V10 < 160] <- 7
qb$ydsr[qb$V10 >= 160 & qb$V10 < 180] <- 8
qb$ydsr[qb$V10 >= 180 & qb$V10 < 200] <- 9
qb$ydsr[qb$V10 >= 200 & qb$V10 < 220] <- 10
qb$ydsr[qb$V10 >= 220 & qb$V10 < 240] <- 11
qb$ydsr[qb$V10 >= 240 & qb$V10 < 260] <- 12
qb$ydsr[qb$V10 >= 260 & qb$V10 < 280] <- 13
qb$ydsr[qb$V10 >= 280 & qb$V10 < 300] <- 14

qb$tds2 <- qb$V11*5

qb$pts <- qb$yds+qb$tds1+qb$ydsr+qb$tds2

rb$yds[rb$V5 < 20] <- 0
rb$yds[rb$V5 >= 20 & rb$V5 < 40] <- 1
rb$yds[rb$V5 >= 40 & rb$V5 < 60] <- 2
rb$yds[rb$V5 >= 60 & rb$V5 < 80] <- 3
rb$yds[rb$V5 >= 80 & rb$V5 < 100] <- 4
rb$yds[rb$V5 >= 100 & rb$V5 < 120] <- 5
rb$yds[rb$V5 >= 120 & rb$V5 < 140] <- 6
rb$yds[rb$V5 >= 140 & rb$V5 < 160] <- 7
rb$yds[rb$V5 >= 160 & rb$V5 < 180] <- 8
rb$yds[rb$V5 >= 180 & rb$V5 < 200] <- 9
rb$yds[rb$V5 >= 200 & rb$V5 < 220] <- 10
rb$yds[rb$V5 >= 220 & rb$V5 < 240] <- 11
rb$yds[rb$V5 >= 240 & rb$V5 < 260] <- 12
rb$yds[rb$V5 >= 260 & rb$V5 < 280] <- 13
rb$yds[rb$V5 >= 280 & rb$V5 < 300] <- 14

rb$td1 <- rb$V6*5

rb$yds2[rb$V9 < 20] <- 0
rb$yds2[rb$V9 >= 20 & rb$V9 < 40] <- 1
rb$yds2[rb$V9 >= 40 & rb$V9 < 60] <- 2
rb$yds2[rb$V9 >= 60 & rb$V9 < 80] <- 3
rb$yds2[rb$V9 >= 80 & rb$V9 < 100] <- 4
rb$yds2[rb$V9 >= 100 & rb$V9 < 120] <- 5
rb$yds2[rb$V9 >= 120 & rb$V9 < 140] <- 6
rb$yds2[rb$V9 >= 140 & rb$V9 < 160] <- 7
rb$yds2[rb$V9 >= 160 & rb$V9 < 180] <- 8
rb$yds2[rb$V9 >= 180 & rb$V9 < 200] <- 9
rb$yds2[rb$V9 >= 200 & rb$V9 < 220] <- 10
rb$yds2[rb$V9 >= 220 & rb$V9 < 240] <- 11
rb$yds2[rb$V9 >= 240 & rb$V9 < 260] <- 12
rb$yds2[rb$V9 >= 260 & rb$V9 < 280] <- 13
rb$yds2[rb$V9 >= 280 & rb$V9 < 300] <- 14

rb$td2 <- rb$V10*5

rb$pts <- rb$yds + rb$td1 + rb$yds2 + rb$td2

wr$yds[wr$V6 < 20] <- 0
wr$yds[wr$V6 >= 20 & wr$V6 < 40] <- 1
wr$yds[wr$V6 >= 40 & wr$V6 < 60] <- 2
wr$yds[wr$V6 >= 60 & wr$V6 < 80] <- 3
wr$yds[wr$V6 >= 80 & wr$V6 < 100] <- 4
wr$yds[wr$V6 >= 100 & wr$V6 < 120] <- 5
wr$yds[wr$V6 >= 120 & wr$V6 < 140] <- 6
wr$yds[wr$V6 >= 140 & wr$V6 < 160] <- 7
wr$yds[wr$V6 >= 160 & wr$V6 < 180] <- 8
wr$yds[wr$V6 >= 180 & wr$V6 < 200] <- 9
wr$yds[wr$V6 >= 200 & wr$V6 < 220] <- 10
wr$yds[wr$V6 >= 220 & wr$V6 < 240] <- 11
wr$yds[wr$V6 >= 240 & wr$V6 < 260] <- 12
wr$yds[wr$V6 >= 260 & wr$V6 < 280] <- 13
wr$yds[wr$V6 >= 280 & wr$V6 < 300] <- 14

wr$td1 <- wr$V7*5

wr$yds2[wr$V9 < 20] <- 0
wr$yds2[wr$V9 >= 20 & wr$V9 < 40] <- 1
wr$yds2[wr$V9 >= 40 & wr$V9 < 60] <- 2
wr$yds2[wr$V9 >= 60 & wr$V9 < 80] <- 3
wr$yds2[wr$V9 >= 80 & wr$V9 < 100] <- 4
wr$yds2[wr$V9 >= 100 & wr$V9 < 120] <- 5
wr$yds2[wr$V9 >= 120 & wr$V9 < 140] <- 6
wr$yds2[wr$V9 >= 140 & wr$V9 < 160] <- 7
wr$yds2[wr$V9 >= 160 & wr$V9 < 180] <- 8
wr$yds2[wr$V9 >= 180 & wr$V9 < 200] <- 9
wr$yds2[wr$V9 >= 200 & wr$V9 < 220] <- 10
wr$yds2[wr$V9 >= 220 & wr$V9 < 240] <- 11
wr$yds2[wr$V9 >= 240 & wr$V9 < 260] <- 12
wr$yds2[wr$V9 >= 260 & wr$V9 < 280] <- 13
wr$yds2[wr$V9 >= 280 & wr$V9 < 300] <- 14

wr$td2 <- wr$V10*5

wr$pts <- wr$yds + wr$td1 + wr$yds2 + wr$td2

useqb <- qb[c(1,2,18)]
userb <- rb[c(1,2,17)]
usewr <- wr[c(1,2,17)]

colnames(useqb) <- c("name","team", "pts")
colnames(userb) <- c("name","team", "pts")
colnames(usewr) <- c("name","team", "pts")

all <- rbind(useqb,userb,usewr)

all$week <- rep(c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16), each = 20)
all$position <- rep(c("qb","rb","wr"), each=320)
all$leader <- rep(c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20), times=48)

```


```{r jitter, echo=FALSE, warning=FALSE, message=FALSE}

## getting jitter
all$jitter <- runif(320, min = -.5, max = .5) 
all$week.j <- all$jitter + all$week

pal <- c("red", "springgreen3", "blue")
plotly::plot_ly(data = all, x = ~week.j, y = ~pts, color = ~position, colors = pal, size = ~pts, text = ~name, alpha=.5)

```
