---
title: 
author: ''
date: '2021-06-12'
slug: our-team
categories: []
tags: [who, people, about]
---

```{r logo1, echo=FALSE, out.width= "35%", out.extra='style="float:right; padding:5px"'}

library(fontawesome)
knitr::include_graphics("erg3.svg")
```

e`r fontawesome::fa("r-project")`g was founded in 2022 by John Kulas (aka "John-o"), an Industrial and Organizational Psychologist. The foundation of the consultancy is on Statistical and Psychometric applications. The services provided are delivered within a systems-oriented framework of Organizational Development. The mission of e`r fontawesome::fa("r-project")`g includes a continuation of collaboration and mentorship for graduate students in Industrial and Organizational Psychology, and these students and former students contribute to e`r fontawesome::fa("r-project")`g's services via structured contract assignments. Dr. Kulas' [resume can be accessed here](Kulas vita.pdf). 

## Contact e`r fontawesome::fa("r-project")`g:{#contact}

<form
  action="https://formspree.io/f/mrgvpwqd"
  method="POST"
>
  <label>
    Your message:
  <textarea name="message"></textarea>
  </label>
<br />
<br />
  <label>
    ...and your email (so we may respond):
    <input type="email" name="email">
  </label>
  <!-- your other form fields go here -->
  <button type="submit">Send</button>
</form>

John-o Kulas:  
`r fontawesome::fa("phone-volume")` 651-216-3353  
`r fontawesome::fa("envelope")` [jtkulas@ergreports.com](mailto: jtkulas@ergreports.com)  
`r fontawesome::fa("square-twitter")` [@jtkulas](https://twitter.com/jtkulas)  
`r fontawesome::fa("location-dot")` Minneapolis, MN 55421 

```{r include=FALSE}
library(leaflet)
library(dplyr)
library(reticulate)
```

```{r, echo=FALSE, warning=FALSE}

content <- paste(sep = "<br/>",
  "<b><a href='https://ergreports.com/'>eRg HQ</a></b>",
  "Minneapolis, MN",
  "55421"
)

ergIcon <- makeIcon(
  iconUrl = "https://ergreports.com/images/erg2.png",
  iconWidth = 60, iconHeight = 50,
  iconAnchorX = 30, iconAnchorY = 30,
)

hc_gdpr <- leaflet() %>%
  setView(lng= -93.24649681376336, lat=44.99948959471243, zoom=5) %>%
#   addTiles() %>%
 addProviderTiles(
    "Stamen.Toner",
    group = "Stamen.Toner"
  ) %>%
 addWMSTiles(
    "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
    layers = "nexrad-n0r-900913",
    options = WMSTileOptions(format = "image/png", transparent = TRUE, opacity = 0.35),
    attribution = "Weather data © IEM Nexrad") %>%
    addMarkers(-93.23, 45.0, icon=ergIcon, popup=content)
  #    addCircleMarkers(-93.23, 45.0, popup=content, radius=20)
  #  addPopups(-93.23, 45.0, content,
#    options = popupOptions(closeButton = FALSE)
#)


htmlwidgets::saveWidget(hc_gdpr, "hc_gdpr.html", selfcontained = TRUE, knitrOptions = list())
hc_gdpr
## helpful(?) for interactive plots in GitPages sites:

## http://ryankuhn.net/blog/How-To-Use-Plotly-With-Jekyll

## https://bookdown.org/nicohahn/making_maps_with_r5/docs/leaflet.html

```
