---
title: 
author: ''
date: '2021-06-13'
slug: home
image:
  caption: ""
  focal_point: ""
  preview_only: yes
---

```{r logo1, echo=FALSE, out.width= "35%", out.extra='style="float:left; padding:5px"'}

library(fontawesome)
knitr::include_graphics("erg3.svg")
```

We are an organizational consulting group staffed by Industrial and Organizational Psychologists and fully [powered by `r icons::fontawesome("r-project")`](https://cran.r-project.org/). Our expertise includes Psychological assessment and statistical consultation, survey creation and administration, and feedback report generation.  

## Services Provided:  

```{r logo2, echo=FALSE, out.width= "45%", out.extra='style="float:right; padding:5px"'}
knitr::include_graphics("erg3.svg")
```

We assist with customized assessment projects, but additionally provide three foundational services:

+ Building and sustaining [engaged workforces](https://ergreports.com/workforce-engagement/)  
+ [Data visualization](https://ergreports.com/testing/)
+ Transitioning existing functions to more cost effective [`r icons::fontawesome("r-project")`-driven  processes](https://ergreports.com/references/)

