---
title: 
author: ''
date: '2021-06-13'
slug: home
image:
  caption: ""
  focal_point: ""
  preview_only: yes
---

```{r logo1, echo=FALSE, out.width= "35%", out.extra='style="float:left; padding:5px"'}

library(fontawesome)
knitr::include_graphics("erg3.svg")
```

We are an [`r icons::fontawesome("r-project")`-powered](https://cran.r-project.org/) organizational consulting group staffed by Industrial and Organizational Psychologists. We specialize in Psychological assessment and statistical consultation, survey creation and administration, and feedback report generation.  

## Services Provided:  

```{r logo2, echo=FALSE, out.width= "45%", out.extra='style="float:right; padding:5px"'}
knitr::include_graphics("erg3.svg")
```

In addition to customized assessment projects, we focus on three fundamental services:

+ developing and fostering an [engaged workplace](https://ergreports.com/workforce-engagement/)  
+ [data visualization](https://ergreports.com/testing/)
+ helping create [`r icons::fontawesome("r-project")`-driven solutions and processes](https://ergreports.com/references/)

